---
title: "Convincing you how bad London weather is!"
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Harriet Laing
Ref1: University of Stellenbosch, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(readr)
library(lubridate)
#Example_data <- Texevier::Ex_Dat

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.
#write_rds(Example_data, path = "data/Example_data.rds")

source("code/ReadLondonDataCSV.R")

LondonData <- ReadLondonDataCSV("data/London/london_weather.csv")

source('code/LondonRainPlot.R')

source('code/LondonTempPlot.R')
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

This is just a quick overview of why the weather in London is bad! The average rainfall way exceeds South Africa and the average temperature is way lower! Just look at these figures from the last ten years...


```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "", fig.ext = 'png', fig.height = 3, fig.width = 6}
LondonRainPlot <- LondonPlot(data= LondonData) 

LondonRainPlot  

```

You can see by the annual precipitation that it only came close to South Africa in 2005! And you can see in 2014 it was EXTREMELY high!
```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "", fig.ext = 'png', fig.height = 6, fig.width = 7}
LondonTempPlot(data=LondonData)
```

Therefore, I am sure you can clearly see how poorly the weather of London looks in comparison to SA! Please do not emigrate...

