---
title: "Evolution of Covid outbreak"
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Harriet Laing^[]
Ref1: Univeristy of Stellenbosch, Cape Town, South Africa
#Email1: 21617023@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

library(tidyverse)
library(lubridate)
library(readr)

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

#write_csv(CovidData, path = "Question1/data/Covid/owid-covid-data.csv")

source("code/ReadCovidDataCSV.R")

CovidData <- ReadCovidDataCSV(dataroot="data/Covid/owid-covid-data.csv")

source("code/CovidAfricaPlot.R")

source("code/CovidSmokingPlot.R")

source("code/CovidWorldAverage.R")

source('code/HospitalICUPlot.R')
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

This report looks at descriptive statistics to understand the evolution of Covid-19 in 2020. First, the impact of Covid on Africa countries is investigated, then the countries with a high prevalence of smoking and then how quickly different regions increased hospital facilities as Covid-19 continued throughout the 2020 year.

# Data  {-}

The data that is used is from Our World in Data and was subsetted to our period of interest which is 2020.

## Investigating the misconception of the experience of African countries with Covid compared with other regions.

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "", fig.ext = 'png', fig.height = 3, fig.width = 6}


CovidAfricaPlot(CovidData)


```

## Countries with high prevalence of smoking & severity of Covid

According to World Population Review, the countries that have the highest prevalence of smoking are:

Nauru (52.10%)
Kiribati (52.00%)
Tuvalu (48.70%)
Myanmar (45.50%)
Chile (44.70%)
Lebanon (42.60%)
Serbia (40.60%)
Bangladesh (39.10%)
Greece (39.10%)
Bulgaria (38.90%)

Compare these countries with highest prevalence of smoking to the world average of new deaths in 2020 from Covid.

```{r}


CovidSmokingPlot <- CovidSmokingPlot(CovidData)

CovidWorldAverage <- CovidWorldAverage(CovidData)

CovidSmokingPlotFinal <- CovidSmokingPlot + geom_hline(yintercept = 0.034218, color='blue', size=1.5) + geom_text(aes(max(location), 0.034218,label = "World average", vjust = - 1), col = "blue")

CovidSmokingPlotFinal
```

## How quickly did different regions increase hospitalisation facilities? 

Did that time series of hospital beds lead or lag on ICU admission rates? By removing the na values, we subset the data to begin at March 8th.

According to the figures, we can see that generally the rates of hospitalisations were similar to rates of ICU admission, and occasionally led on ICU admission. Oceania was excluded because not enough data, and other regions are missing one of the values due to data constraints.

## Asia
```{r}
AsiaHospitalICUPlot <- HospitalICUPlot(Continent="Asia") + labs("Asia weekly hospital admissions and weekly ICU admissions")
AsiaHospitalICUPlot
```

## Africa
```{r}
AfricaHospitalICUPlot <- HospitalICUPlot(data=CovidData, Continent="Africa") + labs("Africa weekly hospital admissions and weekly ICU admissions")
AfricaHospitalICUPlot
```

## Europe
```{r}
EuropeHospitalICUPlot <- HospitalICUPlot(data=CovidData, Continent="Europe") + labs("Europe weekly hospital admissions and weekly ICU admissions")
EuropeHospitalICUPlot
```

## North America
```{r}
NorthAmericaHospitalICUPlot <- HospitalICUPlot(data=CovidData, Continent="North America") + labs("North America weekly hospital admissions and weekly ICU admissions")
NorthAmericaHospitalICUPlot
```

## South America
```{r}
SouthAmericaHospitalICUPlot <- HospitalICUPlot(data=CovidData, Continent="South America") + labs("South America weekly hospital admissions and weekly ICU admissions")
SouthAmericaHospitalICUPlot
```



